Thesis outline

### 2017-06-05 KellyDouglass/Thesis/Thesis_sections/GV.tex
GV chapter

@@

\subsection{Optical data --- SDSS}
%  - KIAS-VAGC (morphological classification)
% Should we use NSA for abs. mag. instead?
SDSS \citep{Abazajian09} (absolute magnitudes courtesy of the MPA-JHU 
catalog\footnote{http://www.mpa-garching.mpg.de/SDSS/DR7/})

The KIAS Value-Added Galaxy Catalog 
\citep[KIAS-VAGC]{Choi10} attempted to calculate a morphological class and type 
for all galaxies in SDSS DR7 based on the color $u-r$, color gradient 
$\Delta (g-r)$, and inverse concentration index.

\subsection{UV data --- GALEX}
\citep{Martin05}

@@

\section[Results]{Results}

@@

Preliminary analysis of mine reveals a population of galaxies that lie in the 
Green Valley on the NUV$-r$ color-magnitude diagram, identified independent of 
their location on the diagram.  I find that, rather than being 
classified based on arbitrary limits placed on the NUV$-r$ values, the galaxies 
can be easily separated into three distinct populations based on the galaxies' 
morphological types as calculated in the KIAS-VAGC; this can be seen in Fig. 
\ref{fig:NUVr_CMD}.  Defined by the $u-r$ color and the color gradient 
$\Delta (g-i)$, it is novel that an estimate of the morphological type of the 
galaxies is an adequate classification for the three populations of the NUV$-r$ 
CMD.  In addition, Fig. \ref{fig:NUVr_hist} shows a histogram of the galaxies 
which overlap in both GALEX and SDSS, separated by their morphological 
classification from the KIAS-VAGC.  It shows that the three populations are well 
fit by three Gaussians --- the new population in the middle is the transient 
galaxy population originally ``missing'' from the optical CMD.

@@

\subsection{Large-scale environmental dependence of dwarf galaxy evolution}

Estimates of the gas-phase chemical abundances of galaxies probe their 
integrated star formation histories, which can provide insight into the 
enrichment of the ISM and CGM.  Dwarf galaxies ($M_r > -17$) have a 
slightly different evolutionary history than galaxies of large stellar masses, 
especially when looking at environmental factors.  The lower stellar masses of 
these galaxies makes them more susceptible to damage from galactic interactions 
and supernovae feedback, since they have smaller gravitational potential wells.  
My current work involves studying the large-scale environmental dependence of 
the chemical evolution of dwarf galaxies \citep{Douglass17a,Douglass17b}.  I estimate gas-phase 
metallicities (the oxygen abundance of a galaxy relative to hydrogen) with the 
Direct $T_e$ method, known for its accuracy and unbiased results.  This method 
``directly'' estimates the temperature of the electrons in an H{\sc ii} 
region from a ratio of the [O{\sc iii}] $\lambda$4363 aural line and the 
[O{\sc iii}] $\lambda \lambda$4959,5007 doublet \citep[as discussed in][this ratio 
is sensitive to the temperature of the ionized gas in an H{\sc ii} 
region]{Osterbrock89,Douglass17a}; with the temperature and density, abundance estimates can 
be made based on emission line ratios from the galaxy.  It can be very difficult 
to use, however, as it relies on a relatively strong detection of the weak [O 
{\sc iii}] $\lambda 4363$ auroral line --- the uncertainty in the measured flux 
of this emission line is the greatest source of error when using this method to 
estimate the chemical abundances.  Consequently, it is used most often on blue, 
star-forming galaxies.  A detailed description of the Direct $T_e$ method can be 
found in \cite{Douglass17a}.  We use a BPT diagram \citep{Baldwin81} to determine if a 
galaxy is star-forming or has traces of an AGN in its spectrum.  BPT diagrams 
measure the hardness of a galaxy's spectrum based on the relationship between 
ratios of some of the galaxy's emission lines.  Our star-forming classification 
is a result of the work done by \cite{Brinchmann04}.

A few of the galaxies for which I am able to estimate metallicities reside in 
the green valley.  When compared with the metallicities of galaxies in the blue 
sequence and red cloud, Fig. \ref{fig:Z_hist} shows that the star-forming green 
valley galaxies have much lower oxygen abundances than star-forming galaxies in 
the blue sequence and red cloud.  With nitrogen abundances that fall within the 
same range as the other two galaxy populations, this shift causes the N/O ratio 
to be much higher in green valley galaxies than in the others.

% Histogram of metallicity for red, blue, green galaxies
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/Z12logOH_I06relations_SF_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/N12logNH_I06relations_SF_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/logNO_I06relations_SF_t3}
    \caption[Distribution of gas-phase chemical abundances in cross-matched SDSS 
    DR7 -- GALEX galaxies]{Histograms of the oxygen abundance (top left), 
    nitrogen abundance (top right), and N/O ratio (bottom center) of the 
    cross-matched SDSS DR7 -- GALEX galaxies (both dwarf galaxies and brighter 
    systems), separated into their locations on the NUV$-r$ color-magnitude 
    diagram according to the morphological type listed in the KIAS-VAGC.  It is 
    readily apparent that the green valley galaxies have much lower oxygen 
    abundances than those in the blue sequence or red cloud.  This, therefore, 
    corresponds to them having the highest N/O values of the three categories.}
    \label{fig:Z_hist}
\end{figure}

When we separate the galaxies in each of the three populations by their 
large-scale environment, we discover a variation in these populations as a 
function of luminosity.  Galaxies are divided into one of two categories for 
their large-scale environment: voids or walls (more dense regions) based on the 
void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  As we see in Fig. 
\ref{fig:Mr_bin}, the fraction of galaxies in the green valley depends on the 
large-scale environment, even at fixed stellar mass or luminosity.  A larger 
fraction of wall dwarf galaxies are found in the green valley than for void 
dwarf galaxies.

@@

@@

\section[Discussion]{Discussion}

\subsection{Morphological classification and gas content indicators}

% classical classification of morphology v. aimc (aimc appaers to be a good indication of the transition in galaxy evolution
% Are there other markers in the gas content of these galaxies?

The morphological classification that we use to isolate the green valley 
population is relatively unique in that it is analytic; morphological 
classification attempts are often completed in a more subjective manner 
\citep[such as the GalaxyZoo,][]{Lintott11}.  In particular, the 
morphological type provided in KIAS-VAGC is a combination of the color $u-r$ and 
the color gradient $\Delta (g-i)$.  Both these quantities are independent of the 
NUV$-r$ CMD, which is part of the novelty behind why this measure separates the 
galaxies into the three evolutionary stages of the CMD so well.

%I also plan to search for other markers in the gas content of the galaxies in 
%the green valley.  
If a galaxy's star formation is quenched due to a loss of 
cold gas, then its H{\sc i} content will be lower than other galaxies of a 
similar stellar mass and large-scale environment.  If it is quenched due to a 
high gas temperature (from AGN or supernovae feedback), then the temperature of 
the gas will be higher than others of a similar size.  These factors will also 
help to determine when and why a galaxy transitions from star-forming to 
quiescent (and maybe back to star-forming).

\subsection{Testing for evidence of AGN feedback}

During my estimation of the chemical content of galaxies with $M_r > -20$, I 
note that the oxygen abundances of galaxies classified as AGN by their 
emission line ratios in the BPT diagrams exhibit extremely low oxygen abundances 
(but normal nitrogen abundance values) when compared to star-forming galaxies of 
a similar stellar mass and large-scale environment.  The same abundance 
signature is seen in the the oxygen and nitrogen abundance results seen in Fig. 
\ref{fig:Z_hist} of the green valley galaxies.  This might indicate a 
link between some dwarf green valley galaxies and a host AGN.  This 
would support other studies of the transition of galaxies from the blue sequence 
to the red cloud, which attribute the quenching of star formation to accretion 
of a central black hole.

I expect to find a large-scale environmental effect on the star formation 
quenching mechanism in addition to the AGN effects.  Giving us feedback on the 
role of the environment in a galaxy's evolution, these results will have great 
impact on the input parameters of large hydrodynamic simulations.  This project 
will serve as an example of the possible science that will be able to be done 
with the future James Webb Space Telescope.

@@

\section[Conclusion]{Conclusion}

>>>>

\section[Theory]{Calculating the color of a galaxy}

A galaxy's color is the ratio of the flux emitted by the galaxy in two different 
bands.  The stellar population of a galaxy will determine its color --- redder 
galaxies contain much older, cooler stars, while the spectrum of a bluer galaxy 
is produced by light from much younger, hotter stars.  A galaxy's color is 
independent of its redshift, so only photometry is needed to calculate the 
ratio.  While the KIAS-VAGC catalog (described below in Section \ref{sec:SDSS}) 
provides the $u-r$ color for all galaxies in SDSS, we make use of the Petrosian 
fluxes in the NSA (described in Section \ref{sec:GALEX}) to calculate the 
UV--optical color.  The NUV$-r$ color is calculated by
\begin{equation}
    \text{NUV}-r = -2.5\log \left( \frac{f_{NUV}}{f_r} \right)
\end{equation}
where $f_{NUV}$ is the Petrosian flux in the NUV-band of GALEX, and $f_r$ is the 
Petrosian flux in the $r$-band of SDSS.

@@

We use the photometric data from SDSS (optical) and GALEX (ultraviolet) as 
cross-matched in the NSA.

\subsection{Optical data --- SDSS}\label{sec:SDSS}
% Should we use NSA for abs. mag. instead? - yes, but not for the thesis

The SDSS Data Release 7 \citep[DR7]{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey.  It uses drift scanning to map approximately 
one-quarter of the northern sky.  A dedicated 2.5-meter telescope at the Apache 
Point Observatory in New Mexico takes photometric data in the five-band SDSS 
system --- $u$, $g$, $r$, $i$, and $z$ \citep{Fukugita96,Gunn98}.  Galaxies with 
a Petrosian $r$-band apparent magnitude $m_r < 17.77$ are selected for 
spectroscopic analysis \citep{Lupton01,Strauss02}.  Gas-phase chemical 
abundances are calculated via the Direct $T_e$ method using emission-line fluxes 
measured by the MPA-JHU catalog\footnote{Available at 
\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in Douglass \& 
Vogeley (2017, in prep).  The large-scale environment of the galaxies is based 
on the void catalog compiled by \cite{Pan12}.  This void catalog is constructed 
from SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which 
are located within the identified voids are labeled as void galaxies; those 
which do not reside in a void are designated as wall galaxies.  Because the 
minimum diameter of a void is defined as 10 \hMpc , the large-scale environment 
of galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
described, so their environment is labeled as unknown.

% KIAS-VAGC (morphological classification)
The Korea Institute for Advanced Study Value-Added Galaxy Catalog 
\citep[KIAS-VAGC]{Choi10} contains galaxies from the SDSS DR7 main sky survey 
based on the New York University Value-Added Galaxy Catalog Data Release 7 
\citep[NYU-VAGC]{Blanton05}.  It provides a morphological class and type 
following the automated morphology classification scheme of \cite{Park05}, using 
the color $u-r$, color gradient $\Delta (g-r)$, and inverse concentration index.  
We use the absolute magnitudes as listed in the KIAS-VAGC.

\subsection{UV data --- GALEX}\label{sec:GALEX}
The Galaxy Evolution Explorer \citep[GALEX]{Martin05} is an orbiting space 
telescope conducting an extra-galactic ultraviolet all-sky survey.  The 
instrument allows imaging and spectroscopic observations in two ultraviolet 
bands --- Far UV (FUV, 1350--1780\AA) and Near UV (NUV, 1770--2730\AA) 
\citep{Morrissey07}.  The NUV-$r$ colors used in this study are calculated from 
the azimuthally-averaged SDSS-style Petrosian fluxes provided in the NASA-Sloan 
Atlas version 0.1.2 \citep[NSA]{Blanton11}.

@@

\section[Results]{Classification of galaxies in the color-magnitude diagram}

@@

@@

This analysis reveals a population of galaxies that lie in the Green Valley on 
the NUV$-r$ color-magnitude diagram, identified independent of their location on 
the diagram.  Rather than being classified based on arbitrary limits placed on 
the NUV$-r$ values \citep[as done by][]{Schawinski14,Salim14a}, the galaxies can 
be easily separated into three distinct populations based on the galaxies' 
morphological types as calculated in the KIAS-VAGC; this can be seen in Fig. 
\ref{fig:NUVr_CMD}.  Defined by the $u-r$ color and the color gradient 
$\Delta (g-i)$, it is novel that an estimate of the morphological type of the 
galaxies is an adequate classification for the three populations of the NUV$-r$ 
CMD.  In addition, Fig. \ref{fig:NUVr_hist} shows a histogram of the galaxies 
which overlap in both GALEX and SDSS, separated by their morphological 
classification from the KIAS-VAGC.  It shows that the three populations are well 
fit by three Gaussians --- the new population in the middle is the transient 
galaxy population originally ``missing'' from the optical CMD.

% classical classification of morphology v. aimc (aimc appaers to be a good indication of the transition in galaxy evolution
The morphological classification that we use to isolate the green valley 
population is relatively unique in that it is analytic; morphological 
classification attempts are often completed in a more subjective manner 
\citep[such as the GalaxyZoo,][]{Lintott11}.  In particular, the 
morphological type provided in KIAS-VAGC is a combination of the color $u-r$ and 
the color gradient $\Delta (g-i)$.  Both these quantities are independent of the 
NUV$-r$ CMD, which is part of the novelty behind why this measure separates the 
galaxies into the three evolutionary stages of the CMD so well.

\subsection{Properties of the Green Valley Galaxies}

\subsubsection{Stellar mass}

\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/GV/Mstar_hist}
    \caption[Stellar mass distribution by morphological type]{The distribution 
    of stellar mass for all galaxies in SDSS DR7, separated by their 
    morphological type.  The galaxies in the green valley have stellar masses 
    comparable to those in the red cloud.  The stellar masses of those galaxies 
    in the blue sequence range from the lowest mass objects up through the 
    stellar masses of the green valley galaxies.}
    \label{fig:M_hist}
\end{figure}

If the green valley galaxies represent those galaxies transitioning between the 
blue sequence and red cloud, then their stellar masses should overlap the masses 
in both these populations.  The distribution of the stellar masses for the 
galaxies in SDSS DR7 is shown in Fig. \ref{fig:M_hist}.  We can see that the 
galaxies in the green valley have stellar masses comparable to those in the red 
cloud.  The stellar masses of those galaxies in the blue sequence range from the 
lowest mass objects up through the stellar masses of the green valley galaxies.  
The distribution of stellar masses of galaxies in the blue sequence should be 
much broader than the range of masses seen in the red cloud galaxies, since 
those in the blue sequence are forming stars and slowly building up their mass.  
Galaxies in the red cloud are fairly stagnant in their star formation, so the 
range of stellar masses of these galaxies will be more narrow than that of the 
blue sequence.  If the green valley galaxies are transitioning between the two 
populations due to a quenching of star formation or a sudden burst of star 
formation, then we would expect their mass range to cover the high-mass end of 
the blue sequence and most of the red cloud.  Indeed, this is what we see in 
Fig. \ref{fig:M_hist}.

\subsubsection{Star formation rates}

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/SFR_hist}
    \includegraphics[width=0.49\textwidth]{Images/GV/sSFR_hist}
    \caption[(s)SFR distribution by morphological type]{The distribution of SFR 
    (left panel) and sSFR (right panel) for all galaxies in SDSS DR7, separated 
    by their morphological type.  The green valley galaxies occupy the 
    intermediate SFRs, while galaxies in the red cloud have low SFRs and 
    galaxies in the blue sequence have higher SFRs.  The same ranges exist for 
    the sSFRs, although the green valley galaxies extend well into the range of 
    sSFRs occupied by the galaxies in the red cloud.}
    \label{fig:SFR_hist}
\end{figure}

Again, if green valley galaxies are transitioning between the blue sequence and 
red cloud, then they should have intermediate (s)SFRs.  The distribution of SFR 
and sSFR for the galaxies in SDSS DR7 are shown in Fig. \ref{fig:SFR_hist}, with 
the galaxies separated by their morphological types.  We see that the 
distribution of SFRs for galaxies in the green valley peaks around 
$\log(\text{SFR}) \sim -0.5$, in between the ranges occupied by the red cloud 
and blue sequence galaxies.  A similar distribution is shown for the sSFRs, 
although the green valley galaxies extend well into the range of sSFRs occupied 
by the galaxies in the red cloud.  \cite{Salim14a} describes transitional 
galaxies (those in the green valley) to have lower sSFRs than galaxies in the 
blue sequence, specifically $-11.8 < \log(\text{sSFR}) < -10.8$.  While our 
results do indicate that the green valley galaxies have lower sSFRs than those 
in the blue sequence, we find that their sSFRs extend well into the red cloud 
range, or to $\log(\text{sSFR}) \sim -12$.

\subsubsection{Gas-phase chemical abundances}

% Histogram of metallicity for red, blue, green galaxies
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/Z12logOH_I06relations_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/N12logNH_I06relations_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/logNO_I06relations_t3}
    \caption[Distribution of gas-phase chemical abundances in cross-matched SDSS 
    DR7 -- GALEX galaxies]{Histograms of the oxygen abundance (top left), 
    nitrogen abundance (top right), and N/O ratio (bottom center) of the 
    cross-matched SDSS DR7 -- GALEX galaxies, separated into their locations on 
    the NUV$-r$ color-magnitude diagram according to the morphological type 
    listed in the KIAS-VAGC.  It is readily apparent that the green valley 
    galaxies have higher nitrogen abundances than those in the blue sequence 
    (and some of the red cloud).  This, therefore, corresponds to them having 
    high N/O ratios.}
    \label{fig:Z_hist}
\end{figure}

Estimates of the gas-phase chemical abundances of galaxies probe their 
integrated star formation histories, which can provide insight into the 
enrichment of the ISM and CGM.  A few of the galaxies for which Douglass \& 
Vogeley (2017, in prep) are able to estimate metallicities reside in the green 
valley.  When compared with the metallicities of galaxies in the blue sequence 
and red cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have 
higher nitrogen abundances than star-forming galaxies in the blue sequence (and 
some of the red cloud).  With oxygen abundances that fall within the same range 
as the other two galaxy populations, this shift causes the N/O ratio to be much 
higher in green valley galaxies than in the blue sequence.

\subsubsection{Large-scale environment}

@@

When we separate the galaxies in each of the three populations by their 
large-scale environment, we discover a variation in these populations as a 
function of luminosity.  As we see in Fig. \ref{fig:Mr_bin}, the fraction of 
galaxies in the green valley depends on the large-scale environment, even at 
fixed stellar mass or luminosity.  A larger fraction of faint wall galaxies are 
found in the green valley than for faint void galaxies.

@@

\section[Discussion]{Understanding green valley galaxies}

Galaxies in the green valley are described to be in a transitional period of the 
galaxy's life cycle, where they are being quenched in their star formation or 
are beginning to form stars after being quiescent.  Here, we are able to 
quantitatively define galaxies in the green valley of the UV-optical CMD.  We 
find them to be of comparable stellar mass to galaxies in the red cloud, have 
intermediate SFRs and intermediate-to-low sSFRs, and have higher gas-phase 
nitrogen abundances and N/O ratios than galaxies in the blue sequence.

The stellar mass range of galaxies in the green valley in Fig. \ref{fig:M_hist} 
shows us that these galaxies have completed most of their star formation.  They 
have acquired enough stars to have converted most of their gas into heavier 
elements.  Combined with the intermediate SFRs and intermediate-to-low sSFRs 
seen in Fig. \ref{fig:SFR_hist}, this tells us that these galaxies are no longer 
forming stars at a high rate.  This is most likely due to an extinction of 
available cool gas from which to form stars.  These galaxies are reaching a 
natural point in their evolution where they transition from an active star 
formation period to a quieter, more quiescent lifestyle.

As explained in \cite{Douglass17b}, nitrogen is thought to be produced in both a 
primary and secondary stage, depending on the presence of other heavy elements.  
The fact that the galaxies in the green valley have higher nitrogen abundances 
compared to those in the blue sequence indicate that they are building up a 
surplus of nitrogen, most likely due to the presence of heavier elements at the 
later star formation episodes.  The surplus of heavier elements allows the CNO 
cycle to commence earlier in the stars' lifetimes, producing nitrogen at a 
higher rate than oxygen.  It is also possible that the higher nitrogen 
abundances are a sign that the galaxies' intermediate mass stars (those 
primarily responsible for nitrogen synthesis) have expired.  This surplus of 
nitrogen results in the high N/O ratios seen for the green valley galaxies in 
Fig. \ref{fig:Z_hist}.

Fig. \ref{fig:Mr_bin} shows that a higher fraction of faint wall galaxies are in 
the green valley than faint void galaxies.  This would indicate that void 
galaxies are slightly behind wall galaxies in their evolution, matching 
predictions based on the $\Lambda$CDM cosmology.  These results also coincide 
with the observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, in 
prep).  They find that, for dwarf galaxies ($M_r > -17$), those which exist in 
voids may have commenced their star formation at a later time and have not 
experienced the same cosmic downsizing as dwarf galaxies residing in denser 
regions.  The higher fraction of wall dwarf galaxies in the green valley might 
also point to an environmental influence on the reason for transitioning through 
the green valley, such as ram pressure stripping, which would occur much less 
frequently in the void environment.  However, the existence of void galaxies in 
the green valley indicate that galaxy interactions cannot be the only quenching 
mechanism.

\subsection{Gas content indicators}

% Are there other markers in the gas content of these galaxies? 
If a galaxy's star formation is quenched due to a loss of cold gas, then its 
H{\sc i} content will be lower than other galaxies of a similar stellar mass and 
large-scale environment.  \cite{Schawinski14} finds that 48\% of the late-type 
galaxies they define to be in the green valley have \ion{H}{1} detections in the 
ALFALFA survey, consistent with a high probability of gas resevoir retention.  
Likewise, \cite{Catinella12} shows that the gas fraction ($M_{\ion{H}{1}}/M_*$) 
correlates with the NUV$-r$ color, suggesting that the transition of galaxies 
into the green valley is not due to an abrupt change in the galaxy's neutral gas 
supply.  If it is quenched due to a high gas temperature (from AGN or supernovae 
feedback), then the temperature of the gas will be higher than others of a 
similar size.  These factors will also help to determine when and why a galaxy 
transitions from star-forming to quiescent (and maybe back to star-forming).

\subsection{Evidence of AGN feedback}

During my estimation of the chemical content of galaxies with $M_r > -20$, I 
note that the oxygen abundances of galaxies classified as AGN by their 
emission line ratios in the BPT diagrams exhibit higher nitrogen abundances 
(but normal oxygen abundance values) when compared to star-forming galaxies of 
a similar stellar mass and large-scale environment.  The same abundance 
signature is seen in the the oxygen and nitrogen abundance results seen in Fig. 
\ref{fig:Z_hist} of the green valley galaxies.  This might indicate a 
link between green valley galaxies and a host AGN.  This would support other 
studies of the transition of galaxies from the blue sequence to the red cloud, 
which attribute the quenching of star formation to accretion of a central black 
hole \citep[e.g.,][]{Croton06,Stasinska08}.

@@

\section[Conclusions]{Conclusions}

We can define galaxies which are transitioning through the green valley of the 
color-magnitude diagram by combining the galaxy's color, color gradient, and 
inverse concentration index.  Galaxies with a magnitude less than 25 for the 
morphological type as calculated in the KIAS-VAGC exist in the green valley 
portion of the UV-optical color magnitude diagram.  Galaxies defined as early 
types (morphological type values equal to 1 or 2) are in the red cloud, while 
those with morphological type values greater than 25 are in the blue sequence.  
With this quantitative definition for galaxies transitioning through the green 
valley, we can begin to understand the properties of green valley galaxies and 
the evolution of galaxies.

Based on our analysis, green valley galaxies have stellar masses comparable to 
those in the red cloud.  They have intermediate SFRs, and low-to-intermediate 
sSFRs.  Green valley galaxies also have high gas-phase nitrogen abundances (N/H), 
resulting in high N/O ratios.  While their SFRs show that something has quenched 
their star formation, their stellar masses inform us that this is not due to any 
premature quenching mechanism.  The high nitrogen abundances in the green valley 
galaxies indicates that the galaxies are either no longer forming stars (since 
nitrogen is produced in lower mass stars than oxygen), or that the galaxies were 
able to produce both primary and secondary nitrogen (heavy elements were present 
during the last few star formation episodes to permit the CNO cycle to commence 
earlier).  This chemical abundance pattern (normal oxygen, high nitrogen, and 
high N/O ratio) is also seen in galaxies classified as AGN, indicating that the 
galaxies in the green valley have an AGN.

There is a higher fraction of faint wall galaxies in the green valley than in 
the void regions.  In conjunction with the conclusions of \cite{Douglass17b} and 
Douglass \& Vogeley (2017, in prep), this indicates that void dwarf galaxies are 
less evolved than dwarf galaxies in denser environments.  It would be beneficial 
to investigate the small-scale ($\sim 1$ \hMpc) environment of galaxies in the 
green valley, to determine if any interactions are responsible for the 
transitional state.
